Analysis of bulk void regions

### 2014-05-08 cosmic_voids.tex
Including analysis of local minima of the FA
New analysis of FA vs L1 figure, deleting any reference of lambda_th as defined trhough the number of halos

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. In the figure \ref{fig:halos_fractions} we 
calculate fractions of halos within each one of the defined environments 
based upon the FOF catalogue of the simulation and for an extensive \lth 
range. Then we look for some key feature that could indicated us a 
possible optimal value of the \lth value. One first step forward our quest 
is the behaviour of the V-web scheme compared with the T-web. As was 
previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
in the figure \ref{fig:halos_fractions}, V-web scheme is significantly more
sensible to variations of the $\lambda_{th}$ value, since all fractions of
halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
for the T-web scheme, fractions change smoothly throughout all \lth range 
covered. From this, it is then expected that the optimal \lth value for 
the V-web scheme is less than the T-web value.

The more notorious characteristic of the figure \ref{fig:halos_fractions} 
is the behaviour of the fraction of halos within sheet regions for both 
web schemes, increasing until a local maximum, and then decreasing. The 
increasing or decreasing rate of the fraction of halos for some region 
could be interpreted as a measure of the degree of non-linearity of such 
region for some specific \lth value. For example, filaments and knots, 
that are the most non-linear regions of the universe, have a negative rate
for all covered \lth range. In the case of voids, the situation is 
completely opposite, where fractions of halos increase in everywhere. If 
we think in terms of the underlying matter field of the cosmic web, \lth 
is just a cutting parameter between highly non-linear regions (filament 
and knots) and low non-linear (voids and sheets). Furthermore, if we take 
into account that dark matter halos are much more likely to form in highly 
non-linear regions, it is expected the obtained behaviour of the fractions 
of halos for voids, filaments and knots as we increase the \lth value. 
However, the behaviour of the fraction of halos in sheets is less clear,
increasing for low \lth values (such as voids) and decreasing for higher 
\lth values (such as filaments and knots). This indicates the transitional 
character of sheet regions in the cosmic web. Our proposal here is to 
select as optimal \lth the value where the fraction of sheets reaches a
local maximum. According to this, we find for the T-web scheme an optimal 
value $\lambda_{opt}^T = 0.36$ and for the V-web scheme $\lambda_{opt}^V = 
0.20$. In the figure \ref{fig:visual_impression} we show the visual 
impression of the cosmic web along with the density field for different 
\lth values including the optimal values. It can be noticed that the found 
optimal values reproduce well the visual impression.

As we have taken halos as tracers of the cosmic web, we analyse 
distributions of mass and peculiar velocity in order to assign typical 
values to each type of environment. In the figure 
\ref{fig:typical_mass_velocity} we calculate both distributions for both 
web schemes and using the FOF catalogue of the simulation. Thick lines 
correspond to the median of the distribution and filled regions limited by
dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
all halos are within such regions for every \lth value and for each type 
of environment. We rather use median and quartiles as measure of 
dispersion because there are some very unusual and extreme values that 
makes the usual analysis based upon means and standard deviations less 
reliable.

A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
is the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
until high mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, specially for values 
grater than the optimal \lth value, indicating that it is not possible to
assign typical mass ranges to each environment as quantified by this 
scheme. For peculiar velocities, this situation is opposite, where V-web
scheme is much more adequate to assign typical distributions of velocity
to each environment. Although T-web also makes a differentiation in the 
distributions of velocity, this is very slight compared with the V-web 
case. These results can be explained by appealing the physical origin of 
each web scheme. As T-web is based upon the Hessian matrix of the 
potential field, it is expected all quantities related to the potential, 
like density field and distribution of halos mass, are well-differentiated 
among each region, while the V-web scheme, based upon the shear velocity 
tensor, all dynamical quantities, as the peculiar velocity field and the 
distribution of the velocity of halos are also expected to be 
well-differentiated among regions as quantified by this scheme.

@@

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as tracer of the cosmic web}
\label{subsec:FA_web}
%-------------------------------------------------------------------------

@@

As has been established \SRKED{[references]}, both schemes presented in
the previous section (V-web and T-web) for classifying the cosmic web 
present many advantages compared with classification schemes based
completely upon the density field, e.g. a more robust description of the
dynamic a kinematic of the cosmic web, a more reliable quantification of 
the visual impression, among others. With the aim of exploiting all of 
these advantages, we propose here a novel approach to classify voids in
cosmological simulations based entirely on the web schemes.

The original version of the T-web scheme \SRKED{[reference, Hahn]} was not
successful at reproducing the visual impression of the cosmic web, 
however, with the introduction of a threshold parameter \SRKED{[reference, 
Forero-Romero]}, this scheme, and even the V-web \SRKED{[reference, 
Hoffman]}, improved enormously. As this free parameter controls the visual 
impression provided by each scheme, phenomenons like percolation depends 
on it as well. Percolation is one of the key features of the structure of 
void regions, indicating how voids are merged among them, and how they 
permeate all the cosmic web.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field around knots presents 
a very narrow distribution, whereas for the V-web the same distribution is
more spread. This can be explained appealing to the low dispersion of the 
density field compared with the peculiar velocity in highly non-linear 
regions like knots. For more linear regions like voids, the behaviour of 
the FA field is quite similar between both schemes, what is consistent 
with the equivalence of the T-web and the V-web in the linear regime 
\SRKED{[reference, Hoffman]}.

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_3$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to the $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions, the FA index increases as well, maintaining a perfect correlation 
approximately until the optimal threshold value for each scheme. Because 
of the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$. 
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
threshold, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the optimal
threshold is a limit value up to which we can have void regions. For other
type of environment such as sheets, filaments and knots, the $\lambda_1$
eigenvalue does not control their spatial boundaries, so the correlation
with the FA index is no longer valid. The larger dispersion in the 
distribution indicates that contours of the FA field are no longer 
corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
decreases to lower values, indicating the presence of isotropic knots. All
of this allows us to conclude that the distribution of the FA with respect
to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
voids, but also a sort of one-dimensional projection of the global 
structure of the cosmic web, starting in highly isotropic central voids, 
passing through very anisotropic sheets and filaments, until isotropic 
knot regions.

For the distribution of the density with respect to the $\lambda_1$ 
eigenvalue, it can be appreciated an analogous behaviour, where central 
regions of voids present the most under-dense values of the overall cosmic 
web. For outer layers of voids, the density field grows progressively 
until sheets and filaments are reached. However, the dispersion in the 
distributions indicates that the geometry of voids as quantified by both 
web schemes is not compatible with the density field, i.e. contours of the
$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
Then, the density is not a reliable quantity to be used as tracer of voids. 
Furthermore, another advantage of using the FA index instead of the 
density is the non-monotonous behaviour of the FA median value, with a 
local maximum that allows to identify the boundaries of void regions.

@@

%.........................................................................
%FIGURE 1: Fraction of halos in each environment
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}  
  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}

  \captionof{figure}{\small Fractions of halos embedded in each one of 
  the defined environments according to the \lth value. T-web scheme 
  (left panel) and V-web scheme (right panel). The optimal parameters 
  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}

  \label{fig:halos_fractions}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 2: Visual impression of the cosmic web
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}

  \captionof{figure}{\small Visual impression of the density field (left 
  panels), and of each classification scheme with the $\lambda_{th}$ values 
  obtained by our criteria (others panels). The color convention for each 
  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
  (black) - knot. For each web scheme, it has been used the previously 
  established optimal threshold as a reference value, so plots are done 
  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
  2\lambda_{opt}$.}

  \label{fig:visual_impression}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 3: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 4: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb(null).pdf}

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb(null).pdf}

  \captionof{figure}{\small In left panels is shown the visual impression 
  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
  defined types of environment, where voids corresponds to white zones, 
  sheets to gray, filaments to dark gray and finally knots to black regions. 
  In the right panels is shown the fractional anisotropy field for the same 
  slide of the simulation and for each web schemes, where black regions 
  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
  degeneration of low values of FA for knots and central regions of voids, 
  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
  and highly planar sheets.}

@@

%.........................................................................
%FIGURE 5: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

>>>>

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. Therefore, we analyse distributions of mass 
and peculiar velocity in order to assign typical values to each type of 
environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
both distributions for both web schemes and using the FOF catalogue of the 
simulation. Thick lines correspond to the median of the distribution and 
filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
$Q_3$, it means, $50\%$ of all halos are within such regions for every 
\lth value and for each type of environment. We rather use median and 
quartiles as measure of dispersion because there are some very unusual 
and extreme values that makes the usual analysis based upon means and 
standard deviations less reliable.

A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
is the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
and higher mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, indicating that it is 
not possible to assign typical mass ranges to each environment as 
quantified by this scheme. For peculiar velocities, this situation is 
opposite, where V-web scheme is much more adequate to assign typical 
distributions of velocity to each environment. Although T-web also makes 
a differentiation in the distributions of velocity, this is very slight 
compared with the V-web case. These results can be explained by appealing 
the physical origin of each web scheme. As T-web is based upon the Hessian 
matrix of the potential field, it is expected all quantities related to 
the potential, like density field and distribution of halos mass, are 
well-differentiated among each region, while the V-web scheme, based upon 
the shear velocity tensor, all dynamical quantities, as the peculiar 
velocity field and the distribution of the velocity of halos are also 
expected to be well-differentiated among regions as quantified by this 
scheme.

@@

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy as tracer of voids}
\label{subsec:FA_voids}
%-------------------------------------------------------------------------

@@

As has been established \SRKED{[references]}, both web schemes presented 
in the previous section (V-web and T-web) for classifying the cosmic web 
present many advantages compared with classification schemes based
completely upon the density field, e.g. a more robust description of the
dynamic a kinematic of the cosmic web, a more reliable quantification of 
the visual impression, among others. With the aim of exploiting all of 
these advantages, we propose here a novel approach to classify voids in
cosmological simulations based entirely on the web schemes.

The original version of the T-web scheme \SRKED{[reference, Hahn]} was not
successful at reproducing the visual impression of the cosmic web, 
however, with the introduction of a threshold parameter \SRKED{[reference, 
Forero-Romero]}, this scheme, and even the V-web \SRKED{[reference, 
Hoffman]}, improved enormously. As this free parameter controls the visual 
impression provided by each scheme, phenomenons like percolation depends 
on it as well. Although percolation is one of the key features of the 
structure of void regions, indicating how voids are merged among them, and 
how they permeate all the cosmic web, our primal interest here is studying 
properties of single voids. Nevertheless, in the next section we shall 
analyse briefly the percolation phenomenon for both web schemes.

@@

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field near to knots presents 
a very narrow distribution around a local minima, whereas for the V-web 
such distribution is more spread out. This can be explained appealing to 
the low fluctuations of the density field compared with the peculiar 
velocity in highly non-linear regions like knots. For more linear regions 
like voids, the behaviour of the FA field is quite similar between both 
schemes, what is consistent with the equivalence of the T-web and the 
V-web in the linear regime \SRKED{[reference, Hoffman]}.

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_3$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids and they are the more 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions or less isotropic voids, the FA index increases as well, 
maintaining a very reliable correlation approximately until $FA=0.95$. 
This limit value of the FA can be traduced in terms of an optimal \lth, 
where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
with optimal thresholds normally taken in previous works \SRKED{[references]}. 
Due to the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
FA limit, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the 
optimal \lth value is a limit value up to which we can have void regions. 
For other type of environment such as sheets, filaments and knots, the 
$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
correlation with the FA index is no longer valid beyond the threshold 
values, furthermore the larger dispersion of the FA distribution also 
indicates that contours of the FA field are no longer corresponding to 
contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
to lower values, indicating the presence of isotropic knots. All of this 
allows us to conclude that the distribution of the FA with respect to the 
$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
but also a sort of one-dimensional projection of the global structure of 
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

For the distribution of the density with respect to the $\lambda_1$ 
eigenvalue, it can be appreciated an analogous behaviour, where central 
regions of voids present the most under-dense values of the overall cosmic 
web. For outer layers of voids, the density field grows progressively 
until sheets and filaments are reached. However, the dispersion in the 
distributions indicates that the geometry of voids as quantified by both 
web schemes is not compatible with the density field, i.e. contours of the
$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
Then, the density is not a reliable quantity to be used as tracer of our 
voids. Furthermore, another advantage of using the FA index instead of the
density is the non-monotonous behaviour of the FA median value, with a 
local maxima that allows to identify properly the boundaries of voids.

%-------------------------------------------------------------------------
\subsection{Identifying void regions}
\label{subsec:identification}
%-------------------------------------------------------------------------

@@

%.........................................................................
%FIGURE 1: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 2: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

  \captionof{figure}{\small In left panels is shown the visual impression 
  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
  defined types of environment, where voids corresponds to white zones, 
  sheets to gray, filaments to dark gray and finally knots to black regions. 
  In the right panels is shown the fractional anisotropy field for the same 
  slide of the simulation and for each web schemes, where black regions 
  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
  degeneration of low values of FA for knots and central regions of voids, 
  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
  and highly planar sheets. Thin dark red curves correspond to contours of
  $FA=0.95$, which is approximately the transitional FA between voids and
  other cosmological regions.}

@@

%.........................................................................
%FIGURE 3: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering
